Leveraging The Progress in Automated Theorem Proving for Program Synthesis\\ \small{WWTF ICT 2022}

### 2022-03-28 WWTF/main.tex
incorporated remarks

\usepackage{url}
\usepackage{xcolor}

@@

1) Parigot's $\lambda\mu$-calculus~\cite{Parigot1} gives a direct translation of classical proofs with datatypes and is essentially ready for implementation.
However, since non-intuitionistic tautologies like $\neg\forall xA(x)\to \exists x\neg A(x)$ or $A\vee \neg A$ are assigned a program, we lose the realizability of $\exists$ and $\vee$.
{\color{red} unclear: ``are assigned a program''}
As discussed in~\cite{practical}, in practice it is often possible to eliminate the non-intuitionistic fragments.
{\color{red} unclear: ``fragments''}
We aim to establish stronger theoretical guarantees on when this is possible but also more practical benchmarks on the feasibility of this approach, even when realizability is not ensured by a theorem.
{\color{red} unclear: ``more practical benchmarks''}

2) Sometimes classical validity guarantees intuitionistic validity, most famously for $\Pi_2$-formulas in Arithmetic~\cite{Friedman}. There have been various variations of this result, most notably by Schwichtenberg's group~\cite{schwichtenberg}.
We will adapt their work to our more general setting.
{\color{red} Can the previous sentence be made more concrete? Also why we this promising and feasiable?}
%	
%We expect that in practice these approaches will be sufficient in many situations.

>>>>

\usepackage{url}
\usepackage{xcolor}
\usepackage[normalem]{ulem}

@@

1) Parigot's $\lambda\mu$-calculus~\cite{Parigot1} gives a direct translation of classical proofs with datatypes and is essentially ready for implementation.
However, since \sout{non-intuitionistic} {\color{blue}non-constructive} tautologies like $\neg\forall xA(x)\to \exists x\neg A(x)$ or $A\vee \neg A$ \sout{are assigned a program} {\color{blue} are classically provable}, we lose the realizability of $\exists$ and $\vee$.
{\color{red} unclear: ``are assigned a program''}
As discussed in~\cite{practical}, in practice it is \sout{often} {\color{blue} sometimes} possible to eliminate the \sout{non-intuitionistic fragments} {\color{blue} non-constructive reasoning steps from proofs}.
{\color{red} unclear: ``fragments''}
We aim to establish stronger theoretical guarantees on when this is possible but also \sout{more practical benchmarks on the feasibility of} {\color{blue}evaluate} this approach, even when realizability is not ensured by a theorem.
{\color{red} unclear: ``more practical benchmarks''}

2) {\color{blue}Under certain conditions on the specification} \sout{Sometimes} classical validity guarantees intuitionistic validity, most famously for $\Pi_2$-formulas in Arithmetic~\cite{Friedman}. There have been \sout{various} {\color{blue} many} variations of this result, most notably by Schwichtenberg's group~\cite{schwichtenberg}.
\sout{We will adapt their work to our more general setting.} {\color{blue} We will collect, adapt and extend them with regard to our concrete setting. This approach is particularly promising when combined with the following, which allows us to consider altered specifications.}
{\color{red} Can the previous sentence be made more concrete? Also why we this promising and feasiable?}
%	
%We expect that in practice these approaches will be sufficient in many situations.
